---
title: "Explore RBesT package for meta-analysis"
fontfamily: pslatex
output:
  pdf_document: default
---

\setlength{\parindent}{0ex}

##### Authors

Michael H. Andreae, M.D., Department of Anesthesiology & Perioperative Medicine, H187, Penn State Health Milton S. Hershey Medical Center, Penn State College of Medicine, Hershey. PA

\newpage
\setlength{\parindent}{0ex}

```{r, check_install_libraries, echo=FALSE, message=FALSE, eval=TRUE}
# This chunk will check if all requiered libaries are installed 
# and install the missing libraries

# https://cran.r-project.org/web/packages/pacman/vignettes/Introduction_to_pacman.html

## Option 1
if (!require("pacman")) install.packages("pacman", repos='http://cran.us.r-project.org')
pacman::p_load(knitr, ggplot2, tidyverse, RBesT)

## Option 2, 
### if option one causes an error, comment option one and uncomment option 2:

# if (!require("knitr")) install.packages("knitr", repos='http://cran.us.r-project.org')
# if (!require("ggplot2")) install.packages("ggplot2", repos='http://cran.us.r-project.org')
# if (!require("readxl")) install.packages("readxl", repos='http://cran.us.r-project.org')

## Option 3
### if option 1 and option 2 both throw an error, then:

# install the packages knitr, ggplot2, readxl manuallyand 
# set "eval=FALSE"" for this chunk above in the top line


```

```{r, global_options, echo=FALSE}
suppressWarnings(library(knitr))
# set options
opts_chunk$set(fig.width=8, fig.height=4, fig.path='Figs/',
               echo=FALSE, warning=FALSE, message=FALSE)
eval_everything=FALSE
```

```{r libraries}
library(RBesT)
```
# Documentation in Vignettes
An Introduction is presented in vignettes.

```{r Vignettes, eval=FALSE, echo=TRUE}
browseVignettes("RBesT")
```

The package is optimized for clinical trial planning.

